Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-27 paper/tex/appendix.tex
typo in Newman reference

We calculated the first three moments of the stacked $\hat{N}(z)$ distribution of all galaxies and compared it to the moments of the true redshift distribution.  Figure~\ref{fig:moments} shows the residuals of the moments for all codes.  Accuracy of the moments varies widely between codes, raising concerns about the propagation to cosmological analyses.  The DESC SRD \citep{Mandelbaum:2018} lists stringent requirements on how well the mean and variance of tomographic redshift bins must be known for each of the main DESC science cases.  We indicate the Year 1 requirements assuming our true mean redshift of $z=0.701$ as dashed lines.  In this study with representative training data, \annz, \bpz, \cmnn, \tpz, and our pathological \trainz\ estimator meet the Y1 requirement on the mean redshift.  Only \annz, \bpz, \cmnn, and \trainz\ meet both requirements.  One should be concerned that many codes fail to meet this ambitious limit under perfect prior information because all codes are anticipated to do no better under realistically imperfect prior information, and indicates that additional calibration to remove these systamatic offsets \citep[e.~g.~][]{Newman:08} will likely be necessary in order to meet these stringent goals.

>>>>

We calculated the first three moments of the stacked $\hat{N}(z)$ distribution of all galaxies and compared it to the moments of the true redshift distribution.  Figure~\ref{fig:moments} shows the residuals of the moments for all codes.  Accuracy of the moments varies widely between codes, raising concerns about the propagation to cosmological analyses.  The DESC SRD \citep{Mandelbaum:2018} lists stringent requirements on how well the mean and variance of tomographic redshift bins must be known for each of the main DESC science cases.  We indicate the Year 1 requirements assuming our true mean redshift of $z=0.701$ as dashed lines.  In this study with representative training data, \annz, \bpz, \cmnn, \tpz, and our pathological \trainz\ estimator meet the Y1 requirement on the mean redshift.  Only \annz, \bpz, \cmnn, and \trainz\ meet both requirements.  One should be concerned that many codes fail to meet this ambitious limit under perfect prior information because all codes are anticipated to do no better under realistically imperfect prior information, and indicates that additional calibration to remove these systamatic offsets \citep[e.~g.~][]{Newman:2008} will likely be necessary in order to meet these stringent goals.
